Detection and partial characterisation of stellar multiplicity with Gaia

### 2018-08-29 article/ms.tex
minor

>>>>

\begin{figure}
	\includegraphics[width=0.5\textwidth]{figures/rv_sb9_k_comparison_v5.png}
    \caption{}
    \label{fig:rv_sb9_k_comparison}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures/ast_gp_hrd_v5.png}
\caption{}
\label{fig:ast_gp_hrd_v5}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures/hrd_single_star_fraction_hist.png}
\caption{}
\label{fig:hrd_single_star_fraction_hist}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures/rv_apw_unimodal_k_comparison_v5.png}
\caption{}
\label{fig:rv_apw_unimodal_k_comparison_v5}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures/rv_apw_unimodal_kalpha_comparison_v5.png}
\caption{}
\label{fig:rv_apw_unimodal_kalpha_comparison_v5}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures/rv_hrd_single_star_fraction_hist_v5.png}
\caption{}
\label{fig:rv_hrd_single_star_fraction_hist_v5}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures/rv_sb9_k_comparison_v5.png}
\caption{}
\label{fig:rv_sb9_k_comparison_v5}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures/rv_sb9_kalpha_comparison_period.png}
\caption{}
\label{fig:rv_sb9_kalpha_comparison_period}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures/rv_sb9_kalpha_comparison_tau.png}
\caption{}
\label{fig:rv_sb9_kalpha_comparison_tau}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures/rv_soubiran_hist_v5.png}
\caption{}
\label{fig:rv_soubiran_hist_v5}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures/tau_single_wrt_kdt_labels_v5.png}
\caption{}
\label{fig:tau_single_wrt_kdt_labels_v5}
\end{figure}
